\subsection{Loopback Multiplexing}
\label{sec:loopmux}

Smart contract systems truly become interesting when contracts are allowed to
\emph{call each other}. This is not a technically difficult operation: Contracts
simply need to have an additional exit and entry point to allow new queries to
other contracts to be made, and these queries to be responded to. Specifically,
we require contracts to \emph{either} return $\msg{return}{y}$, \emph{or}
$\msg{call}{A, M}$, with the latter invoking a separate contract. we associate a
special return value structure with indicating a new contract address and input
to call, and require contracts to process a specific $\msg{resume}{}$ message.

As for the first time, it is possible for multiple separate contracts to get
called, we domain-separate the randomness source $\eta$.

\begin{algorithmic}
  \Function{$\vn{unmuxZ}_{\vn{loopmux}}$}{$(\sigma^o, \rho^o, \sigma^\pi,
      \rho^\pi, \eta), A$}
    \SplitState{\Let $(\sigma^o.\Sigma, \rho^o.\Rho, \sigma^\pi.\Sigma,
      \rho^\pi.\Rho) \gets \vn{forceInitMaps}($\splitstatebreak$(\sigma^o.\Sigma,
      \rho^o.\Rho, \sigma^\pi.\Sigma, \rho^\pi.\Rho), A, \varnothing)$}
    \SplitState{Let $\eta'$ be a randomness source determinstically and
      collision-resistantally derived from the pair $(\eta, A)$.}
    \State \Return $(\sigma^o.\Sigma(A), \rho^o.\Rho(A), \sigma^\pi.\Sigma(A),
      \rho^\pi.\Rho(A), \eta')$
  \EndFunction
\end{algorithmic}

\subimport*{../uc/tnsfn/}{loopmux}

\sloppy
Unlike before, we cannot invert the multiplexing on an entire transcript, as the
transcript may consist of multiple, separate, sub-contract calls. Instead, we
can invert multiplexing each query/response pair in the transcript itself. We
assume the existence of $\vn{unmuxOracle}$, which take a query-response pair
$(q, r)$, where the query is $\vn{muxPubOracle}(A, q')$ or
$\vn{muxPrivOracle}(A, q')$, and maps it to $(A, (q', r))$.

\fussy
As far as descriptions go, it is crucial to note that the leakage description of
a contract is no longer in isolation: what the contract may leak, depends on
what this contract calls. We will assume instead that each sub-contracts leakage
descriptor is aware that it is being run in a loopback system -- and therefore
we give it the full transcripts, even of sub-contracts being called. The
assumption here is that the contract directly called by the user is also trusted
by this user -- the descriptor it gives should be trusted, not necessarily that
of any further contracts it invoked. It is worth noting that this change of
setting for the descriptor function does not preclude using contracts designed
without loopback systems in mind: As this cannot invoke other contracts, their
old descriptor function can be easily lifted to this setting (a slight caveat is that either the old descriptor needs to
be capable of tolerating unconfirmed transaction transcripts over multiple calls
to the underlying function, or there should exist a function which splits
transcripts into these individual calls).

\begin{algorithmic}
  \Function{$\vn{liftDesc}$}{$A, \vn{desc}$}$(t, X, \transcript_\sigma, \transcript_\rho, w, z)$
    \State \Let $\transcript_\sigma' \gets \vn{map}(\vn{proj}_2 \circ
      \vn{unmuxOracle}, \transcript_\sigma)$
    \State \Let $\transcript_\rho' \gets \vn{map}(\vn{proj}_2 \circ
      \vn{unmuxOracle}, \transcript_\rho)$
    \State \Let $X' \gets \vn{unmuxX}_{\vn{regmux}}(X, A); z' \gets
      \vn{unmuxZ}_{\vn{regmux}}(z, A)$
    \State \Return $\vn{desc}(t, X', \transcript_\sigma', \transcript_\rho', w, z')$
  \EndFunction
\end{algorithmic}
\begin{algorithmic}
  \Function{$\vn{unmuxT}$}{$\transcript, A$}
    \SplitState{\Return $\vn{map}(\vn{proj}_2, \vn{filter}(\lambda(A', \cdot) : A =
      A', $\splitstatebreak$\vn{map}(\vn{unmuxOracle}, \transcript)))$}
  \EndFunction
\end{algorithmic}
\begin{algorithmic}
  \Function{$\vn{unmuxX}_{\vn{loopmux}}$}{$X, A$}
    \State \Let $X' \gets \epsilon$
    \For{$(u, \transcript, z, D) \loopin X$}
      \State \Let $\transcript' \gets \vn{unmuxT}(\transcript, A); z' \gets \vn{unmuxZ}_{\vn{loopmux}}(z, A)$
      \State \Let $X' \gets X' \concat (u, \transcript', z', D')$
    \EndFor
    \State \Return $X'$
  \EndFunction
\end{algorithmic}
\subimport*{../uc/desc/}{loopmux}
\subimport*{../uc/deps/}{loopmux}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
