\begin{functionalitysketch}{$\fsc$}
  The smart contract functionality $\fsc$ allows parties to query a
  deterministic state machine determined by $\tnsfn$ and $\lkgfn$ in a
  ledger-specified order.

  \vspace{1em}\noindent\emph{Executing a ledger view:}

  Starting with an initial state $\jointstate \gets \varnothing$,
  and an empty set of confirmed transactions: For each transaction
  in the ledger's view, if the transaction is unknown, allow the adversary to supply its inputs.
  Next, verify the transaction's dependencies, and that, for $(\jointstate', c, y) \gets
  \tnsfn(\jointstate, \ldots)$, $\jointstate' \neq \bot$. If both are satisfied, update
  $\jointstate$ to $\jointstate'$, and record the transaction as confirmed\ if
  $c$ is $\top$. If an
  execution output is requested, return $y$, or $\bot$ if the execution failed. If, on the other hand, one of the
  preconditions is not satisfied, skip this transaction.

  \vspace{1em}\noindent\emph{Prior to any interaction by $\party$:}

  Compute which transactions have been rejected in $\party$'s view of the ledger
  state, and remove any unconfirmed transactions for $\party$ that (directly
  or indirectly) depend on them.

  \begin{receivesketch}[honest]{post-query}{w}
    Retrieve $\party$'s current view $\partyview$ of the contract. Feed this,
    together with the party identifier, and the input $w$ to $\lkgfn$.

    Ask $\party$ if the leakage description returned is acceptable. If so, query
    the adversary for a unique transaction ID $\tx$, and some adversarial input
    corresponding to the leakage, and the transaction's dependencies. Record the
    original input, the adversarial input, the context returned by $\lkgfn$, and
    the transaction's dependencies as being associated with $\tx$ and $\party$.
    Record the transaction as unconfirmed for $\party$, send
    $\msg{submit}{\tx}$ to $\gledger$, and finally return $\tx$.
  \end{receivesketch}

  \begin{receivesketch}[honest]{check-query}{\tx}
    If $\tx$ is owned by $\party$, and is in their current view of the ledger,
    compute and return the output by executing the ledger view up to $\tx$.\ If
    $\tx$ is not in their ledger view, return $\msg{not-found}{}$.
  \end{receivesketch}
\end{functionalitysketch}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../../main"
%%% End:
